ODGI: scalable tools for pangenome graphs

### 2021-06-01 manuscript/main.tex
Table

\newcommand{\odgi}{ODGI}
\newcommand{\cmd}[1]{{\scriptsize\textrm{#1}}}
\newcommand{\cmdbf}[1]{{\textbf{#1}}}
\newcommand{\topic}[1]{{\cmdbf{#1}}:}
\newcommand{\Rplus}{\protect\hspace{-.1em}\protect\raisebox{.35ex}{\smaller{\smaller\textbf{+}}}}
\newcommand{\pp}{\Rplus\Rplus}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}\xspace}

@@

    Table~\ref{tab:02} shows a comparison of the operations necessary to extract a subgraph using \odgi\ and VG. The
    example consists in extracting the centromeres from a pangenome graph made from 88 haploid, phased human genome
    assemblies from 44 individuals from the Human Pangenome Reference Consortium year 1 assembly (see Data
    Availability), plus the chm13 and GRCh38 reference genomes, for a total of 90 haplotypes. All commands are provided
    in the Supplementary Material.

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
        \processtable{Centromeres extraction comparison using \odgi\ and VG
          \label{tab:02}} {
          \resizebox{.99\columnwidth}{!}{
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}}

>>>>

\newcommand{\odgi}{ODGI}
\newcommand{\FIXME}{\textbf{!!FIXME!!}}
\newcommand{\cmd}[1]{{\scriptsize\textrm{#1}}}
\newcommand{\cmdbf}[1]{{\textbf{#1}}}
\newcommand{\topic}[1]{{\cmdbf{#1}}:}
\newcommand{\Rplus}{\protect\hspace{-.1em}\protect\raisebox{.35ex}{\smaller{\smaller\textbf{+}}}}
\newcommand{\pp}{\Rplus\Rplus}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}\xspace}

@@

    Table~\ref{tab:02} shows a comparison of the operations necessary to extract a subgraph using \odgi\ and VG.

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
      \processtable{Example of performance improvement between
        \cmd{odgi extract} and \cmd{VG something}. Centromere region
        is extracted from CHR ?? of the HPRC year 1
        assembly\citep{HPRC}, i.e., 88 haploid, phased human genome
        assemblies from 44 individuals plus the chm13 and GRCh38
        reference genomes stored in 100GB(?) GFA format. All timings
        were performed on a server class machine on SSD MODEL with X
        GB of RAM and 48 CPU cores (Y x 12 core AMD Opteron) Processor
        MODEL @ 3.3 GHz with 8MB L2 Cache.\FIXME
          \label{tab:02}} {
          \resizebox{.99\columnwidth}{!}{
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}}
